City-GAN: Learning architectural styles using a custom Conditional GAN architecture

### 2019-07-03 paper.tex
Add paper as pdf
ArXiv version

\end{itemize}
\begin{figure}[h]
\includegraphics[width=0.49\columnwidth{}]{"figures/examples/1 Place de Mexico, 75016".jpg}%
\hspace{0.015\columnwidth}%
\includegraphics[width=0.49\columnwidth{}]{"figures/examples/1 Port de la Bourdonnais, 75007".jpg}
\caption{Two examples of pictures that we did not include in our dataset: on the left image there are gaps in the facades, the right one is anomalous (not a facade).}
\label{fig:example_invalid}
\end{figure}

@@

\begin{figure}[h]
\includegraphics[width=\columnwidth]{figures/gan.png}
\caption{Eight random samples from the generator of the regular GAN.}
\label{fig:gan}
\end{figure}

@@

\begin{figure}[h]
\includegraphics[width=\columnwidth]{figures/daniel_net.png}
\caption{Our first attempt at a CGAN. Each column represents one random input to the generator. The rows represent: the average of all cities, Amsterdam, Manhattan, Paris and Vienna. }
\label{fig:daniel_net}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{figures/architectures/maxnet.pdf}
\caption{The architecture of our neural network is inspired by \cite{pytorch_deep_2019}. The difference in our custom architecture is that labels are fed into the generator (top) as well as into the discriminator (bottom) alongside the data.}  % TODO
\label{fig:maxnet}
\end{figure}

@@

\begin{figure}[h]
\includegraphics[width=\columnwidth]{figures/good_hack_final.png}
\caption{Our custom CGAN architecture. Each column represents one random input to the generator. The rows represent: the average of all cities, Amsterdam, Manhattan, Paris and Vienna.}
\label{fig:hack}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.75\linewidth]{figures/good_hack_64.png}
\caption{Our custom CGAN trained on images of size $64\times 64$. Each column represents one random input to the generator. The rows represent: the average of all cities, Amsterdam, Manhattan, Paris and Vienna.}
\label{fig:smaller}
\end{figure}

@@

\begin{figure}[h]
\includegraphics[width=\columnwidth]{figures/good_hack_stanford_dataset.png}
\caption{Our custom CGAN trained on the Stanford dataset. Each column represents one random input to the generator. The rows represent: the average of all cities, Amsterdam, Manhattan, Paris and Vienna.}
\label{fig:stanford_net}
\end{figure}

>>>>

\end{itemize}
\begin{figure}[h]
\includegraphics[width=0.49\columnwidth{}]{figures/examples/1_Place_de_Mexico,_75016.jpg}%
\hspace{0.015\columnwidth}%
\includegraphics[width=0.49\columnwidth{}]{figures/examples/1_Port_de_la_Bourdonnais,_75007.jpg}
\caption{Two examples of pictures that we did not include in our dataset: on the left image there are gaps in the facades, the right one is anomalous (not a facade).}
\label{fig:example_invalid}
\end{figure}

@@

\begin{figure}[h]
\includegraphics[width=\columnwidth]{figures/gan.jpg}
\caption{Eight random samples from the generator of the regular GAN.}
\label{fig:gan}
\end{figure}

@@

\begin{figure}[h]
\includegraphics[width=\columnwidth]{figures/daniel_net.jpg}
\caption{Our first attempt at a CGAN. Each column represents one random input to the generator. The rows represent: the average of all cities, Amsterdam, Manhattan, Paris and Vienna. }
\label{fig:daniel_net}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{figures/architectures/maxnet_final.pdf}
\caption{The architecture of our neural network is inspired by \cite{pytorch_deep_2019}. The difference in our custom architecture is that labels are fed into the generator (top) as well as into the discriminator (bottom) alongside the data.}  % TODO
\label{fig:maxnet}
\end{figure}

@@

\begin{figure}[h]
\includegraphics[width=\columnwidth]{figures/good_hack_final.jpg}
\caption{Our custom CGAN architecture. Each column represents one random input to the generator. The rows represent: the average of all cities, Amsterdam, Manhattan, Paris and Vienna.}
\label{fig:hack}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.75\linewidth]{figures/good_hack_64.jpg}
\caption{Our custom CGAN trained on images of size $64\times 64$. Each column represents one random input to the generator. The rows represent: the average of all cities, Amsterdam, Manhattan, Paris and Vienna.}
\label{fig:smaller}
\end{figure}

@@

\begin{figure}[h]
\includegraphics[width=\columnwidth]{figures/good_hack_stanford_dataset.jpg}
\caption{Our custom CGAN trained on the Stanford dataset. Each column represents one random input to the generator. The rows represent: the average of all cities, Amsterdam, Manhattan, Paris and Vienna.}
\label{fig:stanford_net}
\end{figure}
